---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The purpose of this Vignette is to demonstrate the usage of the `kendall_tau` function, and also to illustrate both the correctness and the efficiency of the `kendall_tau` function.

First, we load the package:
```{r setup}
library(kendall)
```

To use the `kendall_tau` function, the users will need to input a matrix with two columns of real numbers which they want to calculate the Kendall $\tau$ on. Notice that this implementation assumes no ties in each column.
```{r}
X <- matrix(c(4,5,3,1,2,6,8,9,7,10),5,2)
kendall_tau(X)
```

To see that the `kendall_tau` function is implemented correctly, we simulated two columns of 2000 observations without ties and compared the output against that of given by the base R function `cor`.
```{r}
set.seed(20201128)
X <- replicate(2, sample(c(-5000:5000), 2000))
all.equal(kendall_tau(X), cor(X, method = "kendall")[1,2])
```

To compare the efficiency of this implementation with that of base R function `cor`, we will make use of the `bench` package:
```{r}
if(!require(bench)) {
  remotes::install_github("r-lib/bench")
  library(bench)
}
```

Using the same simulated data set as above, we can again compare the efficiency of the two functions using the `mark` function by `bench`.
```{r}
result <- bench::mark(kendall_tau(X), cor(X, method = "kendall")[1,2])
print(result)
```
 The performance metrics are summarized in `result`, and we can see that our `kendall_tau` function is in the order of magnitude of microseconds ($\mu$), whereas the base R `cor` function is in the order of magnitude of miliseconds ($m$). This means that our `kendall_tau` function is at least 100 times faster than the base R `cor` function. This is likely due the the fact that the base R `cor` function is implemented using a $O(n^2)$ time complexity algorithm, whereas our `kendall_tau` function takes full advantage of sorting techniques and has time complexity $O(n log n)$.